\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{needspace}

\setlength{\parindent}{0pt}

\definecolor{accent}{HTML}{2E3A59}

\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
}

\pagestyle{empty}

\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt}

\setlist[itemize]{leftmargin=1.5em, itemsep=2pt, parsep=0pt, topsep=4pt}

\begin{document}

% --- Header ---
{\LARGE\bfseries Eliana Ostrovsky}\par\smallskip
{\large AI Engineering Student}\par\smallskip
Machine Learning \textbullet{} Computer Vision \textbullet{} Reinforcement Learning \textbullet{} LLM Systems\par
\smallskip
Buenos Aires, Argentina\par
\href{mailto:elianaostro@gmail.com}{elianaostro@gmail.com} \,|\, +54 9 11 6666-2752\par
\href{https://github.com/elianaostro}{github.com/elianaostro} \,|\, \href{https://linkedin.com/in/eliana-ostro}{linkedin.com/in/eliana-ostro}

\bigskip

% --- Professional Summary ---
\section*{Professional Summary}

AI Engineering student with hands-on experience developing and deploying machine learning systems, LLM-based workflows, and autonomous agents. Experienced in building production-ready AI tools, integrating cloud infrastructure, and translating business requirements into technical implementations. Ranked in the Top 9\% of the AI Engineering program at Universidad de San Andrés.

% --- Professional Experience ---
\section*{Professional Experience}

\textbf{AI Engineer \,|\, Bouldertech.ia} \hfill Oct 2025 -- Present
\begin{itemize}
    \item Design and implement custom AI solutions using modern ML and LLM technologies.
    \item Deploy and benchmark open-source LLMs (Qwen family) and vision models using Ollama on dedicated servers.
    \item Build RAG pipelines and autonomous web navigation agents using OpenCrawl for automated data extraction.
    \item Containerize AI systems using Docker to ensure reproducible environments.
\end{itemize}

\textbf{Data Analyst \& AI Developer \,|\, Alephee} \hfill May 2025 -- Present
\begin{itemize}
    \item Lead the development of internal AI tools and automation workflows.
    \item Build LLM-powered orchestration agents in n8n integrated with Microsoft Teams, SharePoint, and Azure.
    \item Implement workflows generating structured JSON outputs with integrated validation and security layers.
    \item Query and manage large datasets using Microsoft SQL Server.
    \item Prototype cloud solutions using AWS (Bedrock, SageMaker, S3, EC2).
\end{itemize}

\textbf{ML Intern \,|\, DHC} \hfill 2024
\begin{itemize}
    \item Built predictive models using Machine Learning and Feature Engineering to optimize operations in hospitals and medical centers.
\end{itemize}

\textbf{Teaching Assistant \,|\, Universidad de San Andrés} \hfill 2024 -- 2025
\begin{itemize}
    \item Teaching Assistant for Physics I and Calculus III (Análisis Matemático III).
    \item Prepare and deliver classes, grade exams and lab reports.
\end{itemize}

% --- Engineering Projects ---
\section*{Engineering Projects}

\textbf{Trademark Opposition Management Platform}
\begin{itemize}
    \item Building a full-stack web platform for Argentine lawyers that automates weekly INPI (Instituto Nacional de Propiedad Intelectual) bulletin processing and trademark conflict detection.
    \item Compare new trademark filings against client portfolios using multiple complementary algorithms: fuzzy string matching, phonetic similarity, semantic embeddings, CNN-based visual similarity, and LLM reasoning.
    \item Develop a web interface for lawyers to review flagged conflicts, dispatch notification emails to clients, and track client responses throughout the opposition workflow.
\end{itemize}

\needspace{1\baselineskip}
\textbf{Lane Detection Adaptation for Argentinian Roads \,|\, UdeSA Autonomous Vehicle Project}
\begin{itemize}
    \item Collaborator on Argentina's first research autonomous street vehicle at Universidad de San Andrés (\href{https://udesa.edu.ar/auto-autonomo}{udesa.edu.ar/auto-autonomo}), working with the first autonomous driving research dataset in the region (\href{https://ri.conicet.gov.ar/handle/11336/242774}{CONICET dataset}).
    \item Adapted the CLRerNet state-of-the-art lane detection architecture to Argentinian urban environments using pseudo-labeling.
    \item Designed a Student architecture integrating a ConvLSTM module to improve temporal stability in video sequences.
    \item Optimized a lightweight architecture capable of real-time lane detection in poorly marked urban roads.
\end{itemize}

% \textbf{Reinforcement Learning Flight Control}
% \begin{itemize}
%     \item Developed a control system for a scale aircraft using ROS2 and Micro-ROS on ESP32 hardware.
%     \item Trained RL policies in Gazebo simulations to optimize autonomous gliding behavior.
% \end{itemize}

\textbf{Car Price Prediction}
\begin{itemize}
    \item Performed extensive data engineering including cleaning, feature extraction, and transformation of raw automotive datasets.
    \item Trained and fine-tuned an XGBoost model with systematic hyperparameter optimization to maximize prediction accuracy.
\end{itemize}

\textbf{Autonomous Navigation (PPO)}
\begin{itemize}
    \item Implemented a Proximal Policy Optimization model for self-driving agents in a Unity simulation environment.
\end{itemize}

% --- Research ---
\section*{Research}

\textbf{Anti-inflammatory Effect of Nanoparticles on Blood Vessel Endothelium}
\begin{itemize}
    \item Research internship at the Experimental Thrombosis Laboratory, Institute of Experimental Medicine (CONICET -- Academia Nacional de Medicina, Buenos Aires).
    \item Investigators: Charó Nancy, Schattner Mirta.
\end{itemize}

% --- Education ---
\section*{Education}

\textbf{B.S.\ in AI Engineering \,|\, Universidad de San Andrés}
\begin{itemize}
    \item Expected Graduation: 2027.
    \item Top 9\% of the AI Engineering program.
    \item Top 10\% university-wide.
    \item GPA: 8.74 / 10.0.
\end{itemize}

\textbf{High School Diploma in Natural Sciences (Chemistry \& Biotech) \,|\, ORT Argentina}
\begin{itemize}
    \item Graduated with Honors.
\end{itemize}

% --- Technical Skills ---
\section*{Technical Skills}

\begin{itemize}
    \item \textbf{Programming:} Python, SQL, C++, Java, C, JavaScript, Haskell.
    \item \textbf{Machine Learning:} PyTorch, Computer Vision, Reinforcement Learning (PPO), LLM Systems, RAG.
    \item \textbf{Infrastructure:} Docker, Git, n8n, ROS2, Gazebo, Unity, Ollama.
    \item \textbf{Cloud:} AWS (Bedrock, SageMaker, S3, EC2), Microsoft 365 (SharePoint, Teams, Azure), Google Cloud.
    \item \textbf{Languages:} Spanish (Native), English (C2), Hebrew (Basic).
\end{itemize}

% --- Additional Experience ---
\section*{Additional Experience}

\begin{itemize}
    \item \textbf{Cadena} -- Active participant in this international NGO.
    \item \textbf{Israel Challenge, MASA} -- 4.5-month cultural immersion program in Israel.
    \item \textbf{BBYO Exchange} -- 2-week international relations program in Denver, Colorado, USA.
    \item \textbf{ORT Study Trip} -- 2-week English language and culture program in London, UK.
\end{itemize}

\end{document}
